\propertitle

### 2019-12-01 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-01T15:24:42+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

In an exact calculation based on the two assumptions above, the probability
of the sequences of sample and larger-population activities,
$(\ya_{t}, \yA_{t})$, would involve the joint frequencies of total
activities of sample and larger population $F_{\ya,\yA}$, multiplied by the
number of time bins $T$:
\begin{equation}
  \label{eq:prob_joint_frequencies}
  \underbracket{\prod_{t} \pxx(\ya_{t}, \yA_{t})}_{\mathclap{\textit{prob. of joint sequence}}} \equiv
  \prod_{\ya,\yA} \pxx(\ya, \yA)^{T\,F_{\ya,\yA}} =
  \prod_{\ya,\yA}\bigl[\underbracket{\vphantom{\underline{g}}\yG_{\ya\yA}\;\pxx(\yA)}_{\mathclap{\textit{sampling relation}}}\bigr]^{T\,F_{\ya,\yA}}.
\end{equation}
The reasoning would be similar to that leading to
\eqn~\eqref{eq:prob_frequencies} of appendix~\ref{sec:measure_suff}.
Conditioning on the frequencies $\yf$ of the sample would correspond to
constraining the marginal $\sum_{\yA}F_{\ya,\yA}=\yff_{\ya}$. The
maximum-entropy method approximates $T$ with infinity, thus treating the
probability above as a delta. The result is that
\begin{enumerate*}[label=(\roman*)]
\item the probability for the total activity $\yA$ becomes equal to its
  observed frequency;
\item the frequency of sample activity $\ya$ conditional on
  larger-population activity $\yA$ is constrained to equal the
  hypergeometric distribution $\yG_{\ya\yA}$,
  \eqn~\eqref{eq:conditional_hypergeometric}.
\end{enumerate*}
Without this approximation the latter conditional frequency can differ from
$\yG_{\ya\yA}$, and this is expected if the number of bins $T$ is not much
larger than the number of possible joint possibilities, roughly
$n\times N$. Discrepancies of order $nN/T$ are therefore expected.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-01T17:40:51+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

In an exact calculation based on the two assumptions above, the probability
of the sequences of sample and larger-population activities,
$(\ya_{t}, \yA_{t})$, involves the joint frequencies of total activities of
sample and larger population $F_{\ya,\yA}$, multiplied by the number of
time bins $T$:
\begin{equation}
  \label{eq:prob_joint_frequencies}
  \underbracket{\prod_{t} \pxx(\ya_{t}, \yA_{t})}_{\mathclap{\textit{prob. of joint sequence}}} \equiv
  \prod_{\ya,\yA} \pxx(\ya, \yA)^{T\,F_{\ya,\yA}} =
  \prod_{\ya,\yA}\bigl[\underbracket{\vphantom{\underline{g}}\yG_{\ya\yA}\;\pxxx(\yA)}_{\mathclap{\textit{sampling relation}}}\bigr]^{T\,F_{\ya,\yA}}.
\end{equation}
The reasoning would be similar to that leading to
\eqn~\eqref{eq:prob_frequencies} of appendix~\ref{sec:measure_suff}.
Conditioning on the frequencies $\yf$ of the sample would correspond to
constraining the marginal $\sum_{\yA}F_{\ya,\yA}=\yff_{\ya}$. The
maximum-entropy method approximates $T$ with infinity, thus treating the
probability above as a delta. The result is that
\begin{enumerate*}[label=(\roman*)]
\item the probability and observed frequency for the total activity $\yA$
  are constrained to be equal,
\item the frequency of sample activity $\ya$ conditional on
  larger-population activity $\yA$ is constrained to equal the
  hypergeometric distribution $\yG_{\ya\yA}$,
  \eqn~\eqref{eq:conditional_hypergeometric}.
\end{enumerate*}
Without this approximation the latter conditional frequency can differ from
$\yG_{\ya\yA}$, and this is expected if the number of bins $T$ is not much
larger than the number of possible joint possibilities, roughly
$n\times N$.

The final assumption in the maximum-entropy method regards the form of the
probability $\pxxx(\yA)$ in the expression above.
